A holomorphic approach to branes in twisted~$M$-theory

### 2022-09-01 fivebranes/finite.tex
specialize

\subsection{Finite $N$ index}

Before exhibiting the general formula for the local character of the factorization algebra $\clie_\bu(\cG_{N,c})$ on $\C^3$ we set up some notation. 
As above, we let $\chi_k^{\lie{sl}(2)}$ and $\chi^{\lie{sl}(3)}_{[k,l]}$ denote the highest weight $\lie{sl}(2)$ and $\lie{sl}(3)$ characters. 
We also define the following expression which appears in the denominator in all of our characters
\beqn
d(y_i,y,q) = (1-y_1 q)(1-y_2q)(1-y_3q) .
\eeqn 
To simplify formulas, we will temporarily denote the single particle character for the $N=1$ theory $\Obs_1$ by 
\beqn
g_1 (y_i,y,q) = f_1(y_i,y,q)
\eeqn
where $f_1(y_i,y,q)$ is as in equation \eqref{eqn:6done1} and also denote by 
\beqn
g_2 (y_i,y,q) = f_2(y_i,y,q)
\eeqn
where $f_2(y_i,y,q)$ is as in equation \eqref{eqn:6dtwo}. 
Thus $g_2$ is the single particle local character of $\Obs_2 = \clie_\bu(\cG_{2,c})$.
Finally, for $k \geq 3$ let
%\begin{align*}
%f_k (y_1,y_2,y_3,y,q) & \define q^{3k/2} \left(q \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
%& \left.  - q \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right) .
%\end{align*}
\begin{align*}
g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 (k-2)/2} \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3(k-2)/2} \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
& \frac{\left.  - q^{3(k-1)/2} \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - q^{-1 + 3(k-1)/2} \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
\end{align*}
%and hence the conjectural single particle index for the superconformal theory associated to the Lie algebra $\lie{sl}(2)$.

\begin{thm}
\label{thm:finite}
The local character of the factorization algebra $\clie_{\bu}(\cG_{N,c})$ is
\beqn
\chi_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=2}^N g_k(y_1,y_2,y_3,y,q)\right].
\eeqn
Similarly, the local character of the factorization algebra $\clie_\bu(\til{\cG}_{N,c})$ is 
\beqn
\til{\chi}_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=1}^N g_k(y_1,y_2,y_3,y,q)\right].
\eeqn
\end{thm}
\begin{proof}
By Lemma~\ref{lem:envelope} the character of $\clie_\bu (\cG_{N,c})$ is given by 
\beqn
\chi_N = \text{PExp} \left[f_N\right]
\eeqn
where $f_N$ is the single particle local character.
Thus, it suffices to show that $f_N = \sum_{k = 2}^N g_k$.
Recall that we have the following filtration of the factorization algebra $\clie_\bu(\cG_{N,c})$ given by 
\beqn
\clie_{\bu}(\cG_{2,c}) \leftarrow \clie_{\bu}(\cG_{3,c}) \leftarrow \cdots \clie_\bu (\cG_{N,c}) .
\eeqn
Thus we have the following expression for the associated graded factorization algebra 
\beqn
\text{Gr} \, \clie_{\bu} (\cG_{N,c}) \simeq \bigoplus_{k=2}^N \clie_\bu(\cG^{(k)}.
\eeqn

Thus, it suffices to show that $g_k$ is the single particle index of the factorization algebra $\clie_\bu(\cG_{k,c})$, which is a direct computation.
\end{proof}

@@

\begin{proof}
It suffices to show that at the level of single particle indices one has
\beqn
f_{sugra}(y_i, y, q) = \lim_{N \to \infty} f_N(y_i,y,q) ,
\eeqn
where $f_N = \sum_{k = 1}^N g_k$.

@@

As an immediate corollary we have the following result.
\begin{cor}
For any $N \geq 1$ one has
\beqn
\chi_{sugra}(y_i,y,q) = \til{\chi}_N(y_i,y,q) \mod q^{N+1} .
\eeqn
\end{cor}

>>>>

\subsection{A closed formula for the finite $N$ index}

Before exhibiting the general formula for the local character of the factorization algebra $\clie_\bu(\cG_{N,c})$ on $\C^3$ we set up some notation. 
As above, we let $\chi_k^{\lie{sl}(2)}$ and $\chi^{\lie{sl}(3)}_{[k,l]}$ denote the highest weight $\lie{sl}(2)$ and $\lie{sl}(3)$ characters. 
We also define the following expression which appears in the denominator in all of our characters
\beqn
d(y_i,y,q) = (1-y_1 q)(1-y_2q)(1-y_3q) .
\eeqn 
To simplify formulas, we will temporarily denote the single particle character for the $N=1$ theory $\Obs_1$ by 
\beqn
g_{-1} (y_i,y,q) = f_1(y_i,y,q)
\eeqn
where $f_1(y_i,y,q)$ is as in equation \eqref{eqn:6done1} and also denote by 
\beqn
g_0 (y_i,y,q) = f_2(y_i,y,q)
\eeqn
where $f_2(y_i,y,q)$ is as in equation \eqref{eqn:6dtwo}. 
Thus $g_2$ is the single particle local character of $\Obs_2 = \clie_\bu(\cG_{2,c}) = \clie_{\bu}(\cG_c^{(0)})$.
Finally, for $k \geq 1$ let
%\begin{align*}
%f_k (y_1,y_2,y_3,y,q) & \define q^{3k/2} \left(q \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
%& \left.  - q \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right) .
%\end{align*}
%\begin{align*}
%g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 (k-2)/2} \chi^{\lie{sl}(2)}_{k-2}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3(k-2)/2} \chi^{\lie{sl}(2)}_k(q^{-1/2} y) \right. \\
%& \frac{\left.  - q^{3(k-1)/2} \chi^{\lie{sl}(2)}_{k-3}(q^{-1/2}y) - q^{-1 + 3(k-1)/2} \chi^{\lie{sl}(2)}_{k-1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
%\end{align*}
\begin{align*}
g_k (y_i,y,q) & \define q^{3} \left(q^{1 + 3 k/2} \chi^{\lie{sl}(2)}_{k}(q^{-1/2} y)(y_1 + y_2 + y_3) + q^{3k/2} \chi^{\lie{sl}(2)}_{k+2}(q^{-1/2} y) \right. \\
& \frac{\left.  - q^{3(k+1)/2} \chi^{\lie{sl}(2)}_{k-1}(q^{-1/2}y) - q^{-1 + 3(k+1)/2} \chi^{\lie{sl}(2)}_{k+1} (q^{-1/2} y) (y_1^{-1} + y_2^{-1} + y_3^{-1} ) \right)}{d(y_i,y,q)} .
\end{align*}
%and hence the conjectural single particle index for the superconformal theory associated to the Lie algebra $\lie{sl}(2)$.

\begin{thm}
\label{thm:finite}
Let $N \geq 3$. 
The local character of the factorization algebra $\clie_{\bu}(\cG_{N,c})$ is
\beqn
\chi_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=0}^{N-2} g_k(y_1,y_2,y_3,y,q)\right].
\eeqn
Similarly, the local character of the factorization algebra $\clie_\bu(\til{\cG}_{N,c})$ is 
\beqn
\til{\chi}_{N}(y_1,y_2,y_3,y,q) = \text{PExp}\left[\sum_{k=-1}^{N-2} g_k(y_1,y_2,y_3,y,q)\right].
\eeqn
\end{thm}
\begin{proof}
By Lemma~\ref{lem:envelope} the character of $\clie_\bu (\cG_{N,c})$ is given by 
\beqn
\chi_N = \text{PExp} \left[f_N\right]
\eeqn
where $f_N$ is the single particle local character.
Thus, it suffices to show that $f_N = \sum_{k = 0}^{N-2} g_k$.
Recall that we have the following filtration of the factorization algebra $\clie_\bu(\cG_{N,c})$ given by 
\beqn
\clie_{\bu}(\cG_{2,c}) \leftarrow \clie_{\bu}(\cG_{3,c}) \leftarrow \cdots \leftarrow \clie_\bu (\cG_{N,c}) .
\eeqn
Thus we have the following expression for the associated graded factorization algebra 
\beqn
\text{Gr} \, \clie_{\bu} (\cG_{N,c}) \simeq \bigoplus_{k=0}^N \clie_\bu(\cG^{(k)}).
\eeqn

Thus, we must see that $g_k$ is the single particle index of the factorization algebra $\clie_\bu(\cG^{(k)}_c)$, which is a direct observation using the description of $\cG^{(k)}$ we have given in Proposition \ref{prop:Vj}.
\end{proof}

@@

\begin{proof}
It suffices to show that at the level of single particle indices one has
\beqn
f_{sugra}(y_i, y, q) = \lim_{N \to \infty} \til{f}_N(y_i,y,q) ,
\eeqn
where $\til{f}_N = \sum_{k = -1}^{N-2} g_k$.

@@

As an immediate corollary we have the following result.
\begin{cor}
For any $N \geq 1$ one has
\beqn
\chi_{sugra}(y_i,y,q) = \til{\chi}_N(y_i,y,q) \mod q^{N+1} .
\eeqn
\end{cor}
\begin{proof}
This follows from observing that at the level of single particle states $f_N$ is of order $q^{N}$.
\end{proof}

We can also apply the specialization $y=1, y_3=1$ to $\chi_N$.
\begin{prop}
Upon specializing $y=1,y_3=1$ (so that $y_1 y_2 = 1$) one has the following single particle index
\beqn
f_N (y_1,y_2, y_3=1,y=1,q) = \frac{q^2 + q^3 + \cdots + q^{N}}{1-q} 
\eeqn
\end{prop}
\begin{proof}
By induction it suffices to show that the specialization of the single particle local character $g_k$ of the factorization algebra $\clie_\bu(\cG^{(k)})$ is $q^{k+2} / (1-q)$. 
We have already seen this in the case $k=-1,0$, so it suffices to show this when $k \geq 1$.

First observe that the denominator becomes
\beqn
d(y_1,y_2,y_3=1,y=1,q) = (1-y_1 q)(1-y_2q) (1-q) .
\eeqn

Next, we observe that the numerator of $g_k (y_1,y_2,y_3=1,y=1,q)$ can be factored as
\begin{align*}
q^{3 + 3k/2} \left(q^{-(k+2)/2} + q^{-(k-2)/2} - q^{-k/2} (y_1+y_2) \right) 
& = q^{k+2} (1 + q^2 - q (y_1 + y_2)) \\
& = q^{k+2} (1 - y_1 q) (1-y_2 q) 
\end{align*}
where in the last line we have used $y_1 y_2 = 1$.
The result follows.
\end{proof}
